The Talking Heads Experiment

### 2015-04-27 chap10/chap10.tex
fixed remaining widows and orphans

The earliest attempts to investigate the emergence of syntax date back to 1997, in other words even before 
the first Talking Heads experiment started. The first report 
appeared as a paper in the Artificial Intelligence journal in 1998 \citep{Steels:1998}. 
It was described by the journal editors (Dan Bobrow and 
Mike Brady) as ``obviously in an early stage, but very provocative and suggestive.'' The paper was based on my keynote 
lecture at \textsc{ijcai} 1997 in Nagoya and used a precursor of the pan-tilt cameras built by Tony Belpaeme. 
(see \figref{f:plate7}).

@@

Syntactic schemas describe word groups. They have an associated category which corresponds in linguistic terms to grouping categories like noun-group, verb-group, sentence. The slots in syntactic schemas correspond to syntactic functions (also called grammatical relations) such as subject, object, modifier, complement. They name the roles that certain words or word groups play in the group. The categories used to restrict possible slot-fillers correspond in linguistic terms to syntactic categories like noun, verb, adjective, etc. An example of a syntactic schema is the following:
\begin{verbatim}
Schema-541 
  SLOTS: (syn-slot-51 syn-slot-50) 
  DESCRIPTION-SET: 
      ([syn-slot-50 syn-cat-751] 
       [syn-slot-51 syn-cat-761])
  CONSTRAINTS:
      ((PRECEEDS (>> syn-slot-50) (>> syn-slot-51)))
  CATEGORY: syn-cat-77 
  USE: 10 
  SUCCESS: 3
\end{verbatim}
\end{quote}

Of course, instead of noun, noun-group, subject, etc. computer-generated symbols are used such 
as syn-cat-77, syn-slot-50, etc. The constraints on the schema are represented in terms of
a constraint system. Each constraint
has a dual procedural function: to enforce the constraint when re-enacting the situation
described by a schema or to test the constraint when determining whether a schema fits with a situation. In the present
case only a precedence relation is recorded as a constraint. Agreement, intonation, or morphological
endings, are some other possible constraints on syntactic schemas.

The categories restricting slot-fillers are either themselves defined in terms of schemas
(for example, syn-cat-77 could be the restriction on a slot-filler in another schema), or they
are defined as rules that are applied in a forward-chaining fashion during matching. Two
examples of rules related to the above schema are:
\begin{verbatim}
  rule 101: ([WORD (W U)]) => ([MEMBER syn-cat-761])
  rule 99: ([WORD (W O)]) => ([MEMBER Syn-Cat-751])
\end{verbatim}
Semantic schemas describe the language-specific semantic structures underlying the
meanings of complete word groups. The closest linguistic correspondent to a semantic
schema is the notion of a case-frame. The constraints indicate how the total meaning
is constructed/decomposed into the meaning of the parts. During interpretation such
constraints therefore perform the same role as Montague style semantic interpretation
functions. The slots correspond to cases such as agent, patient, time, distance, or arguments
of semantic functions. The categories used to constrain what can fill a slot correspond
in linguistic terms to selection restrictions like animate, human, edible, future, etc. The
schema has also an associated category for the whole so that hierarchical combination is
possible. An example of a semantic schema is:
\begin{verbatim}
Schema-542
  SLOTS: (sem-slot-51 sem-slot-50)
  DESCRIPTION-SET: 
       ([sem-slot-50 sem-cat-751] [sem-slot-51 sem-cat-761])
  CONSTRAINTS: 
       ((CONJUNCTION (>> sem-slot-50) (>> sem-slot-51)))
  CATEGORY: sem-cat-77
  USE: 10
  SUCCESS: 3
\end{verbatim}
Inference rules such as the following define the selection restrictions:
\begin{verbatim}
  rule 102: ([VISIB v-4111) => ([MEMBER sem-cat-761)
  rule 100: ([VER v-4311) => ([MEMBER sem-cat-751)
\end{verbatim}
Each association in the grammar couples a syntactic schema with a semantic schema.
The association can be used in two directions. If a syntactic schema is recognised, i.e., all its 
constraints are satisfied by the input utterance, the semantic schema is
used to reconstruct its meaning. If a semantic schema is recognised, the syntactic schema
is used to reconstruct the form. The association contains a mapping of the slots in order to
enable this reconstruction. For example, the association combining the above two schemas is: 
\begin{verbatim}
Association-271
  MEANING: Schema-542
  FORM : Schema-541
  MAPPING : ((syn-slot-51 sem-slot-51)
             (syn-slot-50 sem-slot-50))
  USE: 10
  SUCCESS: 3"
\end{verbatim}\citep{Steels:1998}

@@

\begin{figure}[h]
  \centerline{\includegraphics[width=.40\textwidth]{chap10/figs/adam-eve.pdf}}
\centerline{\includegraphics[width=.70\textwidth]{chap10/figs/jack-give.pdf}}
\centerline{\includegraphics[width=.80\textwidth]{chap10/figs/push-jill.pdf}}
\caption{\label{fig:adam-eve}Top: Computer animation of the speaking and hearing agent used in public demonstrations 
of the case experiment. 
Middle: Example of a puppet scene, where Jill gives a block to Jack. It shows the source image (left) and a (partial) 
result of image processing (right). Bottom: Another example of a puppet scene where Jill pushes the block.}
\end{figure}
\clearpage
\subsubsection{Scaling up the vision system}
The vision system of the Talking Heads only dealt with static scenes. This had to be scaled up to
deal with dynamical scenes and event recognition. It was the focal work of 
Jean-Christophe Baillie at the Sony Computer Science Laboratory in Paris, who built a vision system 
called \textsc{peract} \is{\textsc{peract} vision system} inspired by an event-recognition developed by Jeffrey 
Siskind.\footnote{The vision system is described in the Ph.D thesis of J-C Baillie. A summary is found here: 
\cite{Steels:2003}. Inspiration for the event recognition system came 
primarily from the paper by \cite{Siskind:2000}.}
The vision system was decomposed into three subsystems with information flowing both in a bottom-up
(from image to world model) and top-down way (from world model and predictions to image): the subsystems achieved 
object identification, event identification, and derivation of qualitative descriptors.

@@

\begin{figure}[h]
  \centerline{\includegraphics[width=\textwidth]{chap10/figs/comparison.pdf}}
\caption{\label{fig:comparison}Comparison between two different strategies: The top-graph shows the growth in the average number of 
markers for the event-specific marker strategy. 
The bottom two graphs show the average size of the set of markers when analogy is used. As usual, the y-axis shows 
the number of games played. Overall, fewer markers are needed, making the case marking system more efficient 
and thus explaining why we get abstract semantic roles.}
\end{figure}

>>>>

The earliest attempts to investigate the emergence of syntax date back to 1997, in other words even before 
the first Talking Heads experiment started. The first report 
appeared as a paper in the Artificial Intelligence journal as \citet{Steels:1998}. 
It was described by the journal editors (Dan Bobrow and 
Mike Brady) as ``obviously in an early stage, but very provocative and suggestive.'' The paper was based on my keynote 
lecture at \textsc{ijcai} 1997 in Nagoya and used a precursor of the pan-tilt cameras built by Tony Belpaeme. 
(see \figref{f:plate7}).

@@

Syntactic schemas describe word groups. They have an associated category which corresponds in linguistic terms to grouping categories like noun-group, verb-group, sentence. The slots in syntactic schemas correspond to syntactic functions (also called grammatical relations) such as subject, object, modifier, complement. They name the roles that certain words or word groups play in the group. The categories used to restrict possible slot-fillers correspond in linguistic terms to syntactic categories like noun, verb, adjective, etc. An example of a syntactic schema is the following:
\begin{verbatim}
Schema-541 
  SLOTS: (syn-slot-51 syn-slot-50) 
  DESCRIPTION-SET: 
      ([syn-slot-50 syn-cat-751] 
       [syn-slot-51 syn-cat-761])
  CONSTRAINTS:
      ((PRECEEDS (>> syn-slot-50) (>> syn-slot-51)))
  CATEGORY: syn-cat-77 
  USE: 10 
  SUCCESS: 3
\end{verbatim}
Of course, instead of noun, noun-group, subject, etc. computer-generated symbols are used such 
as syn-cat-77, syn-slot-50, etc. The constraints on the schema are represented in terms of
a constraint system. Each constraint
has a dual procedural function: to enforce the constraint when re-enacting the situation
described by a schema or to test the constraint when determining whether a schema fits with a situation. In the present
case only a precedence relation is recorded as a constraint. Agreement, intonation, or morphological
endings, are some other possible constraints on syntactic schemas.

The categories restricting slot-fillers are either themselves defined in terms of schemas
(for example, syn-cat-77 could be the restriction on a slot-filler in another schema), or they
are defined as rules that are applied in a forward-chaining fashion during matching. Two
examples of rules related to the above schema are:
\begin{verbatim}
  rule 101: ([WORD (W U)]) => ([MEMBER syn-cat-761])
  rule 99: ([WORD (W O)]) => ([MEMBER Syn-Cat-751])
\end{verbatim}
Semantic schemas describe the language-specific semantic structures underlying the
meanings of complete word groups. The closest linguistic correspondent to a semantic
schema is the notion of a case-frame. The constraints indicate how the total meaning
is constructed/decomposed into the meaning of the parts. During interpretation such
constraints therefore perform the same role as Montague style semantic interpretation
functions. The slots correspond to cases such as agent, patient, time, distance, or arguments
of semantic functions. The categories used to constrain what can fill a slot correspond
in linguistic terms to selection restrictions like animate, human, edible, future, etc. The
schema has also an associated category for the whole so that hierarchical combination is
possible. An example of a semantic schema is:
\begin{verbatim}
Schema-542
  SLOTS: (sem-slot-51 sem-slot-50)
  DESCRIPTION-SET: 
       ([sem-slot-50 sem-cat-751] [sem-slot-51 sem-cat-761])
  CONSTRAINTS: 
       ((CONJUNCTION (>> sem-slot-50) (>> sem-slot-51)))
  CATEGORY: sem-cat-77
  USE: 10
  SUCCESS: 3
\end{verbatim}

Inference rules such as the following define the selection restrictions:
\begin{verbatim}
  rule 102: ([VISIB v-4111) => ([MEMBER sem-cat-761)
  rule 100: ([VER v-4311) => ([MEMBER sem-cat-751)
\end{verbatim}
Each association in the grammar couples a syntactic schema with a semantic schema.
The association can be used in two directions. If a syntactic schema is recognised, i.e., all its 
constraints are satisfied by the input utterance, the semantic schema is
used to reconstruct its meaning. If a semantic schema is recognised, the syntactic schema
is used to reconstruct the form. The association contains a mapping of the slots in order to
enable this reconstruction. For example, the association combining the above two schemas is: 
\begin{verbatim}
Association-271
  MEANING: Schema-542
  FORM : Schema-541
  MAPPING : ((syn-slot-51 sem-slot-51)
             (syn-slot-50 sem-slot-50))
  USE: 10
  SUCCESS: 3"
\end{verbatim}
% \citep{Steels:1998}
\end{quote}

@@

\begin{figure}[t]
  \centerline{\includegraphics[width=.40\textwidth]{chap10/figs/adam-eve.pdf}}
\centerline{\includegraphics[width=.70\textwidth]{chap10/figs/jack-give.pdf}}
\centerline{\includegraphics[width=.80\textwidth]{chap10/figs/push-jill.pdf}}
\caption{\label{fig:adam-eve}Top: Computer animation of the speaking and hearing agent used in public demonstrations 
of the case experiment. 
Middle: Example of a puppet scene, where Jill gives a block to Jack. It shows the source image (left) and a (partial) 
result of image processing (right). Bottom: Another example of a puppet scene where Jill pushes the block.}
\end{figure}
\clearpage
\subsubsection{Scaling up the vision system}
The vision system of the Talking Heads only dealt with static scenes. This had to be scaled up to
deal with dynamical scenes and event recognition. It was the focal work of 
Jean-Christophe Baillie at the Sony Computer Science Laboratory in Paris, who built a vision system 
called \textsc{peract} \is{\textsc{peract} vision system} inspired by an event-recognition developed by Jeffrey 
Siskind.\footnote{The vision system is described in the Ph.D thesis of J-C Baillie. A summary is found here: 
\cite{Steels:2003}. Inspiration for the event recognition system came 
primarily from the paper by \cite{Siskind:2000}.}
The vision system was decomposed into three subsystems with information flowing both in a bottom-up
(from image to world model) and top-down way (from world model and predictions to image): the subsystems achieved 
object identification, event identification, and derivation of qualitative descriptors.

@@

\begin{figure}[h]
  \centerline{\includegraphics[width=.9\textwidth]{chap10/figs/comparison.pdf}}
\caption{\label{fig:comparison}Comparison between two different strategies: The top-graph shows the growth in the average number of 
markers for the event-specific marker strategy. 
The bottom two graphs show the average size of the set of markers when analogy is used. As usual, the y-axis shows 
the number of games played. Overall, fewer markers are needed, making the case marking system more efficient 
and thus explaining why we get abstract semantic roles.}
\end{figure}

### 2015-04-27 chap12/chap12.tex
fixed remaining widows and orphans

Here is another example of a fitness landscape from the domain of space, developed by 
Michael Spranger.\footnote{These results are documented at length in: \cite{Spranger:2014}.}
It focuses on understanding the role of grammar for optimising spatial language. \is{Spatial Language Game}
The experiment involves \textsc{qrio} humanoids
(see \figref{fig:spatial}) and uses a 
sophisticated vision system developed by Spranger, together with IRL and Fluid 
Construction Grammar (in the previous chapter). A variety of spatial language strategies 
were operationalised, in particular:

\begin{figure}
\centerline{\includegraphics[width=0.8\linewidth]{chap11/figs/spatial.pdf}}
\caption{Set-up for the spatial language game experiments. Two robots are looking at a scene 
with a few blocks, a bigger box with tags indicating front, back or left and right side, and a global landmark in the form 
of a large tag pasted on the wall. {\itshape Top left and right:} World as seen through the camera of the robot. 
{\itshape Bottom left and right:} The internal world model as perceived by the left and right robot.}
\label{fig:spatial}
\end{figure}
\begin{enumerate}
\item The use of {\itshape projective relations} such as front/back, above/below, left/right. This requires imposing a coordinate
system on the world model and name areas within this coordinate system. A common coordinate system is to take 
an object, such as the human body of the speaker as reference point and project vectors emanating from the body. 
\item The use of {\itshape proximal relations} such as far/near. This requires that the distances of objects with respect to the 
reference point are computed and categorised. 
\item The use of {\itshape absolute relations}, such as North/West/East/South, related to global directions. 
\item The use of an {\itshape allocentric landmark} (as opposed to an egocentric one)
from which the situation is conceptualised. For example, in the 
phrase `the block in front of the box', the box is acting as a landmark and the projective spatial relations are 
computed as emanating from that object. Another example is `the block on your left' where the landmark is the 
hearer. 
\end{enumerate}

@@

A study of ongoing change in the vocabularies of human speakers shows that the invention of a brand new wordform happens seldom. 
Usually an existing wordform is recruited to express an uncovered meaning. The meaning of the already existing wordform
expresses aspects of the novel meaning to be expressed but there is not an exact overlap. However, the existing word is sufficiently 
suggestive so that the hearer can guess what meaning is intended by the speaker. For example, the word `mouse' becomes 
adopted for computer mouse based on its appearance. Often a compound of several words is used, each of them suggesting 
other aspects of the meaning, such as `bitcoin', which suggests digital (`bit') and currency (`coin').  
There are several other strategies, for example, an abbreviation of a long word becomes itself a single new word, 
such as `MOOC', meaning `massively open on-line course' and now standing for a course made available through the internet. 
There are also playful variations created with existing words, as for example
`wackadoo' which means `bizarre person' and probably originally came from the word `wacky'.

>>>>

Here is another example of a fitness landscape from the domain of space, developed by 
Michael Spranger.\footnote{These results are documented at length in: \cite{Spranger:2014}.}
It focuses on understanding the role of grammar for optimising spatial language. \is{Spatial Language Game}
The experiment involves \textsc{qrio} humanoids
(see \figref{fig:spatial}) and uses a 
sophisticated vision system developed by Spranger, together with IRL and Fluid 
Construction Grammar (in the previous chapter).
\enlargethispage{1em}
A variety of spatial language strategies 
were operationalised, in particular:

\begin{figure}[b]
\centerline{\includegraphics[width=0.8\linewidth]{chap11/figs/spatial.pdf}}
\caption{Set-up for the spatial language game experiments. Two robots are looking at a scene 
with a few blocks, a bigger box with tags indicating front, back or left and right side, and a global landmark in the form 
of a large tag pasted on the wall. {\itshape Top left and right:} World as seen through the camera of the robot. 
{\itshape Bottom left and right:} The internal world model as perceived by the left and right robot.}
\label{fig:spatial}
\end{figure}
\begin{enumerate}
\item The use of {\itshape projective relations} such as front/back, above/below, left/right. This requires imposing a coordinate
system on the world model and name areas within this coordinate system. A common coordinate system is to take 
an object, such as the human body of the speaker as reference point and project vectors emanating from the body. 
\item The use of {\itshape proximal relations} such as far/near. This requires that the distances of objects with respect to the 
reference point are computed and categorised. 
\item The use of {\itshape absolute relations}, such as North/West/East/South, related to global directions. 
\item The use of an {\itshape allocentric landmark} (as opposed to an egocentric one)
from which the situation is conceptualised. For example, in the 
phrase `the block in front of the box', the box is acting as a landmark and the projective spatial relations are 
computed as emanating from that object. Another example is `the block on your left' where the landmark is the 
hearer. 
\end{enumerate}

@@

\newpage
A study of ongoing change in the vocabularies of human speakers shows that the invention of a brand new wordform happens seldom. 
Usually an existing wordform is recruited to express an uncovered meaning. The meaning of the already existing wordform
expresses aspects of the novel meaning to be expressed but there is not an exact overlap. However, the existing word is sufficiently 
suggestive so that the hearer can guess what meaning is intended by the speaker. For example, the word `mouse' becomes 
adopted for computer mouse based on its appearance. Often a compound of several words is used, each of them suggesting 
other aspects of the meaning, such as `bitcoin', which suggests digital (`bit') and currency (`coin').  
There are several other strategies, for example, an abbreviation of a long word becomes itself a single new word, 
such as `MOOC', meaning `massively open on-line course' and now standing for a course made available through the internet. 
There are also playful variations created with existing words, as for example
`wackadoo' which means `bizarre person' and probably originally came from the word `wacky'.

### 2015-04-27 chap7/chap7.tex
fixed remaining widows and orphans

Ludwig Wittgenstein\is{Wittgenstein} went through two major 
periods in his thinking. During the first period he worked
within the framework of logical empiricism, initiated by 
Bertrand Russell and others at the end of the 19th century. 
The logicist approach defines a language by listing the 
elementary building blocks (the words), the combination 
rules (the syntax), and a mapping from words and 
syntactic structures to semantic interpretations (the semantics).  
It assumes that there is a universal, logical structure to the
world which can be captured once and for all in a
non-ambiguous logical language 
and that the permissible inferences can be catalogued 
exhaustively. This project has its roots in the 
17th century dream of
Leibnitz and Descartes to streamline rational thinking
so that it becomes as clear and non-controversial as
numerical calculation. 
Wittgenstein enthusiastically participated in this project, 
which is still vigorously being pursued today by logicians 
and linguists alike, even though many of them do not necessarily subscribe
to the universalist thesis motivating the early developments of 
logic.\footnote{Wittgenstein's main work from this period is \cite{Wittgenstein:1922}. 
A prototypical example of the logicist research program 
is found in \cite{Carnap:1928}.}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.65\textwidth]{chap7/figs/landscape.pdf}}
\caption{\label{RMF1}Typical segment of a semiotic
landscape capturing the co-occurrence relations between
referents, meanings and word forms. The FM/MF relations are
in thick lines, the RM/MR relations in regular lines, and 
the RF/FR relations in dashed lines.}
\end{figure}

\begin{center}
\begin{table}
\begin{tabular}{ l  l  }
\lsptoprule
{\itshape Label}& {\itshape Relation } \\ \midrule
RM & referent to meaning \\ 
MR & meaning to referent \\ 
FM & form to meaning\\ 
MF & meaning to form\\ 
RF & referent to form \\ 
FR & form to referent  \\ 
\lspbottomrule
\end{tabular}
\caption{\label{tab:7labelrelation}}
\end{table}
\end{center}

The partial landscape in \figref{RMF1} (taken from
an actual experiment) contains an example where the agents use
two possible meanings for conceptualising {\itshape situation2}, namely
[\textsc{gray} 0.0–0.25] (very light) and [\textsc{hpos} 0.5–0.75]
(medium right ). The words `katapu' and `tisame' lexicalise
[\textsc{gray} 0.0–0.25] and `wobo' and `tisame' [\textsc{hpos} 0.5–0.75]. 
Each meaning has therefore two synonyms and `tisame' is 
ambiguous; it can mean both [\textsc{gray} 0.0–0.25]
and [\textsc{hpos} 0.5–0.75]. Three words
are used to communicate the situation: `katapu', `tisame', 
and `wobo'. Such a structure is typical for grounded
lexicon evolution and complexity rapidly increases when the
same meanings are used to communicate about other
situations (which is obviously very common and indeed desirable).

>>>>

Ludwig Wittgenstein went through two major 
periods in his thinking. During the first period he worked
within the framework of logical empiricism, initiated by 
Bertrand Russell and others at the end of the 19th century. 
The logicist approach defines a language by listing the 
elementary building blocks (the words), the combination 
rules (the syntax), and a mapping from words and 
syntactic structures to semantic interpretations (the semantics).  
It assumes that there is a universal, logical structure to the
world which can be captured once and for all in a
non-ambiguous logical language 
and that the permissible inferences can be catalogued 
exhaustively. This project has its roots in the 
17th century dream of
Leibnitz and Descartes to streamline rational thinking
so that it becomes as clear and non-controversial as
numerical calculation. 
Wittgenstein enthusiastically participated in this project, 
which is still vigorously being pursued today by logicians 
and linguists alike, even though many of them do not necessarily subscribe
to the universalist thesis motivating the early developments of 
logic.\footnote{Wittgenstein's main work from this period is \cite{Wittgenstein:1922}. 
A prototypical example of the logicist research program 
is found in \cite{Carnap:1928}.}

@@

\begin{figure}[t]
  \centerline{\includegraphics[width=.65\textwidth]{chap7/figs/landscape.pdf}}
\caption{\label{RMF1}Typical segment of a semiotic
landscape capturing the co-occurrence relations between
referents, meanings and word forms. The FM/MF relations are
in thick lines, the RM/MR relations in regular lines, and 
the RF/FR relations in dashed lines.}
\end{figure}

\begin{table}[b]
\begin{tabular}{ l  l  }
\lsptoprule
{\itshape Label}& {\itshape Relation } \\ \midrule
RM & referent to meaning \\ 
MR & meaning to referent \\ 
FM & form to meaning\\ 
MF & meaning to form\\ 
RF & referent to form \\ 
FR & form to referent  \\ 
\lspbottomrule
\end{tabular}
\caption{\label{tab:7labelrelation}}
\end{table}

The partial landscape in \figref{RMF1} (taken from
an actual experiment) contains an example where the agents use
two possible meanings for conceptualising {\itshape situation2}, namely
[\textsc{gray} 0.0–0.25] (very light) and [\textsc{hpos} 0.5–0.75]
(medium right ). The words `katapu' and `tisame' lexicalise
[\textsc{gray} 0.0–0.25] and `wobo' and `tisame' [\textsc{hpos} 0.5–0.75]. 
Each meaning has therefore two synonyms and `tisame' is 
ambiguous; it can mean both [\textsc{gray} 0.0–0.25]
and [\textsc{hpos} 0.5–0.75].
\enlargethispage{1em}
Three words
are used to communicate the situation: `katapu', `tisame', 
and `wobo'. Such a structure is typical for grounded
lexicon evolution and complexity rapidly increases when the
same meanings are used to communicate about other
situations (which is obviously very common and indeed desirable).

### 2015-04-27 chap8/chap8.tex
fixed remaining widows and orphans

By the way, there's a bug in the 'headnet' software with respect to 
routes; there's a finite limit on the field length for the 'route' 
field. If you make a route that's too long, it gets truncated, so 
you can have an agent whose route goes:\\
	... paris 10 bruss\clearpage
The agent will complete its games on 'paris' and then go into 
stasis waiting for a server called 'bruss' to pick it up. A patch 
for this would probably be nice to have at some point.

@@

3. Masking. Eliminating zero channels should be done on the source not on
value (= value after scaling, so it is often zero). corrected in: 
prototype.lsp (in the functions folder)
\clearpage
After theses patches, sites can be running again.

Fred and Luc.
\end{mail}
\begin{mail}
--============\_-1278188520==\_d============\\
Date: Tue, 29 Jun 1999 23:25:45 +0200 (MET DST)\\
Subject: There is hope for robokind \\

@@

\begin{mail}
--============\_-1278188520==\_d============\\
Date: Wed, 30 Jun 1999 17:16:19 +0200\\
From: Joris Van Looveren <joris@arti.vub.ac.be>\\
Subject: Re: paris site\\

@@

The experiment ended with the following ``tongue-in-cheek'' post by Angus McIntyre on the Forum:
\clearpage
\begin{mail}
{\bfshape 1999-10-14 15:08:29 Angus McIntyre}\\
{\itshape Bad news and good news}\\

>>>>

By the way, there's a bug in the 'headnet' software with respect to 
routes; there's a finite limit on the field length for the 'route' 
field. If you make a route that's too long, it gets truncated, so 
you can have an agent whose route goes:\\
	... paris 10 bruss
The agent will complete its games on 'paris' and then go into 
stasis waiting for a server called 'bruss' to pick it up. A patch 
for this would probably be nice to have at some point.
\enlargethispage{1em}
	A
\end{mail}

@@

3. Masking. Eliminating zero channels should be done on the source not on
value (= value after scaling, so it is often zero). corrected in: 
prototype.lsp (in the functions folder)

After theses patches, sites can be running again.

Fred and Luc.
\end{mail}

\newpage

\begin{mail}
--============\_-1278188520==\_d============\\
Date: Tue, 29 Jun 1999 23:25:45 +0200 (MET DST)\\
Subject: There is hope for robokind \\

@@

Luc
\end{mail}
\newpage
\begin{mail}
--============\_-1278188520==\_d============\\
Date: Wed, 30 Jun 1999 17:16:19 +0200\\
From: Joris Van Looveren <joris@arti.vub.ac.be>\\
Subject: Re: paris site\\

@@

The experiment ended with the following ``tongue-in-cheek'' post by Angus McIntyre on the Forum:

\begin{mail}
{\bfshape 1999-10-14 15:08:29 Angus McIntyre}\\
{\itshape Bad news and good news}\\
